---
title: "ML model on Salary"
author: "Dumi Yambira"
date: "2023-03-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective

The dataset comprises years of experience in relation to salary.The objective is to use ML model of regression to predict estimated salary based on experience.The objective of this short project is to build an ML model based on simple linear regression and to demonstrate the skills in ML

```{r load the data and library, echo=FALSE}
#load the data
datasalary = read.csv('Salary_Data.csv')

#load the library
library(caTools)
library(ggplot2)

```

```{r data pre-processing, echo=FALSE}
#Pre-process the data
set.seed(123)

datasplit = sample.split(datasalary$Salary, SplitRatio = 0.7) # dependent variable

train.data = subset(datasalary, datasplit == TRUE)
test.data = subset(datasalary, datasplit == FALSE)
```

```{r data modelling, echo=FALSE}
#Data modelling stage
#regression for training set
regressor = lm(formula = Salary ~ YearsExperience, data = train.data)

#predict function for test set
data.predict = predict(regressor, newdata = test.data)

```

## Data Visualisation

```{r data evaluation, echo=FALSE}
#evaluate through visualization
ggplot() +
  geom_point(aes(x = train.data$YearsExperience, y = train.data$Salary),
             color = 'red') +
  geom_line(aes(x = train.data$YearsExperience, y = predict(regressor, newdata = train.data)),
             color = 'blue') +
  ggtitle('Salary based on Years of Experience(Training set)') +
  xlab('Years of Experience') +
  ylab('Salary')

```

## Mean Squared Error

```{r accuracy assessment, echo=FALSE}
#Assess the accuracy
mean((regressor$residuals^2)/10000000)
```

# Conclusion

Using the ML model of simple regression, Years of experience in work highly influence the amount of Salary paid. Hence we can predict that more years of experience result in a higher salary in a workplace. MSE (Mean Squared Error) of 2.5 indicates that this model can highly predict the outcome of the actual data and this model can be both valid and reliable in using years of experience as a factor in predicting one\`s salary.
